%-------------------------
% Resume in Latex
% Author : Faiyazthulla Shaik
% Website: https://github.com/faiyazthulla-shaik/Latex_Resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}
\usepackage{fontawesome}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.375in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\href{https://faiyazpdx.vercel.app/}{\Large Faiyazthulla Shaik}} & {\faEnvelope}\href{mailto:faiyaz@pdx.edu}{ faiyaz@pdx.edu}\\ 
  {\faLocationArrow}{ 1818 SW 4th Avenue, Apartment 628, Portland, OR - 97201} & {\faPhone} +1 971-408-5551 \\
{\faLinkedinSquare}\href{https://www.linkedin.com/in/faiyazthulla/} { linkedin.com/in/faiyazthulla} & {\faGithub} \href{https://github.com/faiyazthulla-shaik}{github.com/faiyazthulla-shaik}
\vspace{-5pt}
\end{tabular*}


%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Portland State University}{Portland, OR}
      {Master of Science in Computer Science;  GPA: 3.83/4.00}{Mar. 2022 -- Aug. 2023}
    \vspace{-5pt}
    \resumeSubheading
      {Prasad V Potluri Siddhartha Institute of Technology}{Vijayawada, India}
      {Bachelor of Technology in Computer Science and Engineering;  GPA: 8.06/10.0}{June. 2015 -- Mar. 2019}
    \vspace{-5pt}
  \resumeSubHeadingListEnd

%
%--------Technical Skills and Interests------------
\section{Technical Skills and Interests}
 \resumeSubHeadingListStart
    \resumeSubItem{Languages}
      {Java, Python, HTML+CSS, JavaScript, C/C++}
    \resumeSubItem{Web Dev Technologies/Tools}
      {JSON, jQuery, ReactJs, Bootstrap, VScode, Eclipse, Git, Github, Jenkins}
    \resumeSubItem{Frameworks/Technologies}
      {Spring boot, JUnit, Mockito, Hibernate}
    \resumeSubItem{Cloud/Databases}
      {Amazon Web Services (AWS), Relational Database(MySQL), PostgreSQL, Oracle}
    \resumeSubItem{Areas of Interest}
      {Software Development and Engineering, Cloud Development}
    \resumeSubItem{Soft Skills}
      {Problem-Solving, Self-learning, Presentation, Adaptability}
    \resumeSubItem{Relevant Coursework}
      {Data Structures and Algorithms, Object Oriented Programming, Database Management System, Software Engineering}
 \resumeSubHeadingListEnd

%-----------PROJECTS-----------------
\section{Projects}
  \resumeSubHeadingListStart
    \resumeSubItem{Text Emotion Analysis}
      {Developed a model for emotion detection in English text using machine learning techniques, with a focus on analyzing emotions in textual dialogues. The model utilizes NLP techniques such as Multinomial Naive Bayes Classifier, TF-IDF Vectorizer, Linear SVM, and Logistic Regression. The accuracy of the model is evaluated using labeled tweet data sets.}
    \resumeSubItem{Internet Relay Chat}
      {Created a single server architecture-based application utilizing Python code and deployed it on AWS Cloud by configuring an EC2 instance. Implemented multi-user functionality, enabling users to create and manage groups, as well as broadcast messages within them.}
    \resumeSubItem{Loan Prediction for Commercial Bank}
      {Designed a modeling system that predicts whether the loan can be granted to the customer using Random Forest Machine Learning prediction algorithm.}
%     \resumeSubItem{Mac Setup}
%       {Book that gives step by step instructions on setting up developer environment on Mac OS.}
  \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Portland State University}{Portland, OR}
      {Graduate Teaching Assistant}{Sep. 2022 - June. 2023}
      \resumeItemListStart
        \item {\small Conducted office hours to provide individualized support to students.\vspace{-2pt}}
        \item {\small Drafted detailed weekly reports to the course professor to assist in directing curriculum, planning lessons, assignments, quizzes, final projects, and instructing labs.\vspace{-2pt}}
        \item {\small Demonstrated strong communication, organizational, and time management skills while balancing multiple responsibilities.\vspace{-2pt}}
      \resumeItemListEnd

    \resumeSubheading
      {Tata Consultancy Services}{Hyderabad, India}
      {Software Engineer}{May 2019 - Feb 2022}
      \resumeItemListStart
        \item {\small Migrating and refactored the legacy Java code to optimized Spring boot applications with Jenkins deployment which boosted efficiency.\vspace{-2pt}}
        \item {\small Developed RESTful API services as a middleware between the application and third-party APIs using Java.\vspace{-2pt}}
        \item {\small Ensured application quality by developing comprehensive JUnit test cases enhancing test coverage by 80 percent. \vspace{-2pt}}
        \item {\small Developed \& deployed web services in API model for integrating with various clients which made application scalable. \vspace{-2pt}}
        \item {\small Collaborated closely with Software Architects and Senior Developers to design and implement high-quality software solutions using design. \vspace{-2pt}}
      \resumeItemListEnd
  \resumeSubHeadingListEnd


%-----------Achievements-----------------
\section{\textbf{Achievements}}
\vspace{-0.4mm}
\resumeItemListStart
    \item {\small Received ‘Intercultural Leadership Award’ for mentoring International Students at Portland State University.\vspace{-8pt}}
    \item {\small Achieved a commendable score in the global coding event 'CODE VITA' organized by TCS.\vspace{-8pt}}
    \item {\small Recognized with the 'Best Team Award' for delivering thoroughly tested, bug-free code and making significant contributions to the project at Tata Consultancy Services.\vspace{-8pt}}
\resumeItemListEnd

%-------------------------------------------
\end{document}

